---
title: "LAD_assignment_working"
output: html_document
date: "2024-05-06"
---

Objective:
This markdown is focused on designating run assignment using Length-at-date (LAD) for juveniles passing Red Bluff Diversion Dam (RBDD) via R script. Both CBR and USFWS have shared Length-at-date run designation data. USFWS currently assigns run designation using a macro in Excel & Access but would like to automate via R. 

Data sources:

- CBR shared file: lengthcriteriariver.csv renamed run_designation_cbr.csv 
- USFWS shared file: RunDesignation.csv renamed run_designation_fws.csv
- EDI Data portal - RBDD : https://portal.edirepository.org/nis/mapbrowse?scope=edi&identifier=1365&revision=1
- SacPas LAD figures: https://www.cbr.washington.edu/sacramento/data/delta_salvage.html


Run designation naming: 

- lengthcriteriariver.csv:  "WL"    "WE"    "LFL"   "LFE"   "FL"    "FE"    "SL"    "SE"    "WL.1"  "WE.1"  "LFL.1" "LFE.1" "FL.1"  "FE.1"  "SL.1"  "SE.1" 

- RunDesignation.csv: "F", "L", "W", "S"

- catch.csv: "fall run", "late fall run", "spring run", "winter run", "not reported"

- renamed runs to: "fall", "late_fall", "spring", "winter"

To do: 

- current function assigns response base on presence/absence of date and length. Catch.csv data has run designation for catch_id's with length data but no date. Find methods (likely in macros) to determine how this is designated. 

- Double check method is matching run assingment in catch.csv

- Compare CBR method to USFWS method


Bill Poytress information via email exchange: 

      "Thanks Jen for the update.  And yes LAD assignment is a macro we run within Access, so hard coding it in R would be a lot better for the process.  The one thing to keep in mind, is that we do after the fact genetic corrections in some cases for spring and winter run in the fall period each year.  I wonder if we should actually assign race and then export the csv's to EDI?  Let me know your thoughts on that situation.  Thanks for the update and progress!!"

      "Upon further investigation I found two things regarding run assignment.  A) the rbdd.catch.csv files we have uploaded to EDI include a run designation for all measured fish in the column "run".  B) Fish are designated a runID of "n/p" for all other species and for chinook plus counts that need run assignment through the "Wild_Totals"  macro currently in access that takes the plus count from any given trap and applies the ratio of spring, winter, fall or late-fall fish from the measured fish within a specific sample and applies that value to the plus count fish and then sums them by run.  C) Not sure how the LengthCriteriaRiver.csv file from DWR handles the overlap of foklengths from the original Frank Fisher/Sheila Greene table, but it could be handled differently than the table we use (stored in access) as RunDesignation.  Technically, we followed Johnson et al. 1992 which indicates the value of the forklength overlap should correspond to the later spawning group.    See the table in the access file to confirm, or see the attached, exported copy of the table we use for runID."


```{r load_libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)
```

```{r load_data}
## load LAD designations from CBR and USFWS
lad_cbr <- read.csv(here::here("JPI_convert_to_Rcode/data","run_designation_cbr.csv"))
lad_usfws_raw <- read.csv(here::here("JPI_convert_to_Rcode/data","run_designation_fws.csv"))
lad_fws <- lad_usfws_raw %>% select(2:7)

## load catch.csv from EDI Data portal
# Define the URL by selecting link from EDI Data portal -- catch.csv
url <- "https://portal.edirepository.org/nis/dataviewer?packageid=edi.1365.1&entityid=58540ac4ed34ce05f3309510f4be91e5"

# Download and read the CSV file into a data frame
df_catch_raw <- read.csv(url)
```


```{r wrangle_data}
#wrangle fws to match cbr format
lad_fws<-lad_fws %>% 
 tidyr::separate(LookupDate, into = c("mm", "dd"), sep = "/") %>% 
  mutate(mm = as.numeric(mm),
         dd = as.numeric(dd)) %>% 
 mutate(RunDesignation = recode( RunDesignation, 
         "L" =  "late_fall",
         "F" = 'fall',
         "W" = "winter",
         "S" = "spring"))

#wrangle cbr to match fws format
lad_cbr_long <- lad_cbr %>% 
  mutate(across(c("WL", "WE"), as.character)) %>% 
  pivot_longer(
    cols = -c(MONTH, DAY),
    names_to = c("RunDesignation", "min_max", "suffix"),
    names_pattern = "(.*)(L|E)(\\.1)?",
    names_repair = "minimal"
  ) %>% 
  mutate(value = as.integer(value)) %>% 
  pivot_wider(names_from = c(min_max, suffix), 
              values_from = value) %>% 
  rename(MinLength1 = L_, 
         MaxLength1 = E_, 
         MinLength2 = L_.1, 
         MaxLength2 = E_.1, 
         mm = MONTH, 
         dd = DAY) %>% 
  replace_na(list(MinLength1 = 0, MaxLength1 = 0, MinLength2 = 0, MaxLength2 = 0)) %>% 
   mutate(RunDesignation = recode( RunDesignation, 
         "LF" =  "late_fall",
         "F" = 'fall',
         "W" = "winter",
         "S" = "spring"))


#filter catch.csv to chinook salmon
df_catch <- df_catch_raw %>% 
  filter(common_name == "Chinook Salmon") %>%
  mutate(start_date = lubridate::ymd(start_date)) %>% 
  select(catch_id,common_name, start_date, fork_length, count, run) %>% 
   mutate(run = recode( run, 
         "late fall run" =  "late_fall",
         "fall run" = 'fall',
         "winter run" = "winter",
         "spring run" = "spring",
         "not reported" = "not reported"))

#remove unneeded data  
rm(df_catch_raw)
rm(lad_cbr)
rm(lad_usfws_raw)
```


```{r fct_LAD_designation}
# Function to assign run designation based on LAD data
#lad_data should be formatted with mm dd as numeric columns
#catch_data should have start_date as a date column and fork_length as a numeric column

fct_LAD_designation <- function(lad_data, catch_data){
  
 # Extract the month and day from the start_date column in catch.csv
  catch_data <- catch_data %>%
    mutate(start_date = lubridate::ymd(start_date),
           mm = lubridate::month(start_date),
           dd = lubridate::day(start_date))
 
   # Filter lad_data based on the month, day, and fork_length in catch.csv
  catch_data %>%
    rowwise() %>% 
    mutate(run_designation =  {
      if (is.na(start_date) & is.na(fork_length)) {
        "No length or date"
      } else if (is.na(start_date) & !is.na(fork_length)) {
        "No date"
      } else if (!is.na(start_date) & is.na(fork_length)) {
        "No length"
      } else {
        matches <- lad_data$RunDesignation[
          lad_data$mm == mm & lad_data$dd == dd & 
          ((fork_length >= lad_data$MinLength1 & fork_length <= lad_data$MaxLength1) | 
           (fork_length >= lad_data$MinLength2 & fork_length <= lad_data$MaxLength2))
        ]
        if (length(matches) == 0) {
          "no run designated"
        } else {
          paste(matches, collapse = ", ")
        }
      }
    })
}



#check designations
df_catch_designation_fws <- fct_LAD_designation(lad_data = lad_fws, catch_data = df_catch)
df_catch_designation_cbr <- fct_LAD_designation(lad_data = lad_cbr_long, catch_data = df_catch)

#save data
 # save(df_catch_designation_fws, file =here::here("JPI_convert_to_Rcode/data","catch_run_designation_fws.rda"), compress = "xz")
  
 # save(df_catch_designation_cbr, file =here::here("JPI_convert_to_Rcode/data","catch_run_designation_cbr.rda"), compress = "xz")

```



Comparing data it seems the designation in april for late fall is the main discrepancy between fws and cbr, catch and fws designate late_fall and cbr returns no run designation. Look into april min/max. Outside of those, a few discrepancies with  2/4 fall x spring(cbr) (8), 2/16/14 winter x spring (cbr) (1), 2/11 spring x winter,spring(cbr) (4) Other designation is that
```{r compare_LAD_designation}
# Join the data frames
df_join <- df_catch_designation_fws %>%
  select(start_date, mm, dd, fork_length, run, run_designation_fws = run_designation) %>%
 cbind(run_designation_cbr = df_catch_designation_cbr$run_designation) %>% 
    mutate(year = year(start_date),
         doy = yday(start_date)) 

#for plot
df_join_long <- df_join %>% 
  pivot_longer(cols = c(5:7),
               names_to = "dataset",
               values_to = "run")

# Filter the rows where run, run_designation_fws and run_designation_cbr are not the same
df_different_runs <- df_join %>%
  filter(run != run_designation_fws | run != run_designation_cbr | run_designation_fws != run_designation_cbr) %>% 
  filter(!is.na(fork_length))

# Filter the rows where run_designation_fws and run_designation_cbr are not the same
df_different_runs_cbr.fws <- df_join %>%
  filter( run_designation_fws != run_designation_cbr) %>% 
    filter(!is.na(fork_length))

```

```{r plot_designations, fig.width=12}

lad <- bind_rows(
  lad_fws %>% mutate(dataset = "fws"),
  lad_cbr_long %>% mutate(dataset = "cbr")
)

lad_plot<-lad %>% 
  pivot_longer(cols = c(4:7),
               names_to = "threshold",
               values_to = "length") %>% 
    mutate(date = make_date(year = 2012, month = mm, day = dd),  # set a year
         doy= yday(date)) %>%   # Extract the day of the year
  filter(threshold %in% c("MinLength1")) # "MinLength2" 

#cbr and fws - min1- differ, min 1 & min 2 = full overlap
ggplot(lad_plot, aes(x = doy, y= length) ) +
  geom_point( aes(color = interaction(RunDesignation,dataset), shape = dataset)) +
  scale_shape_manual(values = c(0,16)) 


lad_fws %>% 
  pivot_longer(cols = c(4:7),
               names_to = "threshold",
               values_to = "length") %>% 
    mutate(date = make_date(year = 2012, month = mm, day = dd),  # Create a date for a generic year
         doy= yday(date)) %>%   # Extract the day of the year
  filter(threshold == "MinLength1") %>% # filter(threshold %in% c("MinLength1", "MaxLength1" )) %>% 

ggplot(aes(x = doy, y= length, group = interaction(RunDesignation,threshold))) +
  geom_point(aes(color = RunDesignation)) 

```


```

